Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-20 wearables_survey.tex
rough of questions complete.

\subsubsection{Threat Perceptions}
Before they get to the wearable device question, they must answer these two questions about the Cubetastic3000. people who did not answer these two comprehension questions were filtered out (this was about 4\% of our participants). These questions both filtered out people who were not paying attention, people who were rushing through it for money, etc. \\[-.8cm]

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item Where and when would you wear the Cubetastic3000?
\item What can the Cubetastic3000 do? \\[-.8cm]
\end{itemize}

The purpose of the 6/305 questions were to determine how much the device, data type, and data recipient played a role in determining if a person was upset by an event or not. These are word for word modeled after the mobile user study. You can see that in the first example question, these three controls are highlighted. Other questions were used for calibration with the smartphone study, where we literally ask the same questions as the study, but toggling the device type, to see if this plays a role in risk perception. \\[-.8cm]

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item How would you feel if an app on your Cubetastic3000 learned how you were feeling based on your heart rate and shared that with the public, without asking you first?
\item How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first? \\[-.8cm]
\end{itemize}

@@

Fill in your benefit numbers for the following technologies:\\
Fill in your risk numbers for the following technologies:

Handguns: \_\_\_\_\_\_\_ \\
Motorcycles: \_\_\_\_\_\_\_\\
Lawnmowers: \_\_\_\_\_\_\_\\
Voice-Based Emotion Detection: \_\_\_\_\_\_\_\\
Electricity: \_\_\_\_\_\_\_\\

@@

\subsubsection{User Concerns}
This is an open-ended question. Show the question here. Say that the participants had as much space as they wanted, although they were shown a line.

\subsubsection{Additional Questions}
demographics and IUIPC, explain why I used IUIPC instead of the Westin, just one or two sentences will do.

>>>>

\subsubsection{Threat Perceptions}
Before they get to the wearable device question, they must answer these two questions about the Cubetastic3000. people who did not answer these two comprehension questions were filtered out (this was about 4\% of our participants). These questions both filtered out people who were not paying attention, people who were rushing through it for money, etc.

\textit{Where and when would you wear the Cubetastic3000?}\\[-.5cm]

\textit{What can the Cubetastic3000 do?}

The purpose of the 6/305 questions were to determine how much the device, data type, and data recipient played a role in determining if a person was upset by an event or not. These are word for word modeled after the mobile user study. You can see that in the first example question, these three controls are highlighted. Other questions were used for calibration with the smartphone study, where we literally ask the same questions as the study, but toggling the device type, to see if this plays a role in risk perception.

\textit{How would you feel if an app on your Cubetastic3000 learned how you were feeling based on your heart rate and shared that with the public, without asking you first}\\[-.5cm]

\textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}

@@

\textit{Fill in your benefit numbers for the following technologies:}\\
\textit{Fill in your risk numbers for the following technologies:}

\textit{Handguns}: \_\_\_\_\_\_\_ \\
\textit{Motorcycles}: \_\_\_\_\_\_\_\\
\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
\textit{<New Tech Here>}: \_\_\_\_\_\_\_\\
\textit{Electricity}: \_\_\_\_\_\_\_\\

@@

\subsubsection{User Concerns}
Lastly, after investigating user perceptions of personal threats, general perceptions of risks and benefits, we thought we could just ask the users what they thought were the most likely risks.

\textit{What do you think are the most likely risks associated with wearable devices?}

Take this with a grain of salt since users are not the most accurate at determining which is the most likely, but we can really see what users care about. The participants had as much space as they wanted to write their reply. People were primed for this question because we asked it after the other two sets of questions, but this just means that people have been thinking about it for a while. We were not looking for hard results, but more of inspiration to direct future work and to just check if we were also asking the right questions which captured the people's concerns throughout the survey.

\subsubsection{Additional Questions}
During the exit portion of the survey, we asked for demographics (gender, age, education) along with if the person owns a wearable or not. We thought that would be important to know. Also, we imagined that privacy would be correlated to these results, which is why we made everyone take the IUIPC to see how much they cared about privacy. Explain why I used IUIPC instead of the Westin, just one or two sentences will do (cite the IUPIC paper, and the SOUPS paper on how the Westin is not so accurate).
